A fully labelled proof system for intuitionistic modal logics

### 2020-09-30 FullyLabelled/JLC/soundness.tex
not much in 3-5

We are now ready to state the main theorem of this section, of which
the implication \ref{iii}$\implies$\ref{iv} in
Theorem~\ref{thm:cutfree-compl} is an immediate consequence.

>>>>

We are now ready to state and prove the main theorem of this section, of which
the implication \ref{iii}$\implies$\ref{iv} in
Theorem~\ref{thm:cutfree-compl} is an immediate consequence.
